---
title: "Analysis code for valuing diversity intervention experiment"
output:
  html_document:
    df_print: paged
    toc: true
---

# Setup 

```{r message = FALSE}
pacman::p_load(tidyverse, magrittr, lme4, lmerTest)
pacman::p_install_version("emmeans", "1.4.8")
pacman::p_load_gh("lukaswallrich/rNuggets")

#Contact Lukas Wallrich (l.wallrich@gold.ac.uk | lukas.wallrich@gmail.com) to access the data
df <- read_rds('data_with_conditions.RDS') 
```


```{r}
cohen_d <- function(df, DV, group, na.rm = TRUE) {
    desc <- df %>% rename(group = {{group}}) %>% group_by(group) %>% summarise(M = mean({{DV}}, na.rm = na.rm), var = var({{DV}}, na.rm = na.rm), N = n()) %>% arrange(group)
    out <- tibble::tribble(
      ~pair, ~d)  
    for (i in 1:(nrow(desc)-1)) {
      for (j in (i+1):nrow(desc)) {
        pair <- paste(desc$group[i], "&", desc$group[j])
        sd_pooled <- sqrt(((desc$N[i]-1)*desc$var[i]+(desc$N[j]-1)*desc$var[j])/(desc$N[j]+desc$N[i]-2))
        d <- (desc$M[i] - desc$M[j]) / sd_pooled
        out %<>% rbind(tibble::tibble(pair = pair, d = d))
      }
    }
    return(out)
}

hedges_g <- function(df, DV, group, na.rm = TRUE, ci = .95) {
    df %<>% select({{DV}}, {{group}}) %>% rename(group = {{group}}, DV = {{DV}})
    if (na.rm) df %<>% tidyr::drop_na()
    groups <- df$group %>% unique()  %>% sort()
    out <- tibble::tibble()
    for (i in 1:(length(groups)-1)) {
      for (j in (i+1):length(groups)) {
        pair <- paste(groups[i], "&", groups[j])
        g <- gethedgesg(df$DV[df$group == groups[j]], df$DV[df$group == groups[i]], coverage = ci)
        g$pair <- pair
        out %<>% rbind(g)
      }
    }
    out %>% dplyr::select(pair, dplyr::everything())
}

gethedgesg <-function( x1, x2, design = "between", coverage = 0.95) {
#http://www.tqmp.org/RegularArticles/vol14-4/p242/
  # mandatory arguments are x1 and x2, both a vector of data
require(psych) # for the function harmonic.mean.
# get basic descriptive statistics
ns <- c(length(x1),length(x2))
mns <- c(mean(x1),mean(x2))
sds <- c(sd(x1),sd(x2))
# get pairwise statistics
ntilde <- harmonic.mean(ns)
dmn <- mns[2]-mns[1]
sign_diff <- 1
if(dmn<0) sign_diff <- -1; dmn <- abs(dmn)
sdp <- sqrt( (ns[1]-1) *sds[1]^2 + (ns[2]-1)*sds[2]^2) / sqrt(ns[1]+ns[2]-2)
# compute biased Cohen’s d (equation 1)
cohend <- dmn / sdp
# compute unbiased Hedges’ g ( equations 2a and 3)
eta <- ns[1] + ns[2] - 2
J <- exp ( lgamma(eta/2) - (log(sqrt(eta/2)) + lgamma((eta-1)/2) ) )
hedgesg <- cohend * J
# compute noncentrality parameter (equation 5a or 5b depending on the design)
lambda <- if(design == "between") {
hedgesg * sqrt( ntilde/2)
} else {
r <- cor(x1,x2)
hedgesg * sqrt( ntilde/(2 * (1-r)) )
}
# confidence interval of the hedges g ( equations 6 and 7)
tlow <- qt(1/2 - coverage/2, df = eta, ncp = lambda )
thig <- qt(1/2 + coverage/2, df = eta, ncp = lambda )
dlow <- tlow / lambda * hedgesg
dhig <- thig / lambda * hedgesg
# all done! display the results
(tibble(g = hedgesg, ci.lower = dlow, ci.upper = dhig)*sign_diff) %>% tibble::as_tibble()
#cat("Hedges’g = ", hedgesg, "\n", coverage*100, "% CI = [", dlow, dhig, "]\n")
}

report_anova <- function(x, to_clip = TRUE) {
  out <- x %>% data.frame() %>% rownames_to_column() %>% mutate(report = glue_warn("{rowname}: F({round(DenDF)}, {NumDF}) = {round_(F.value)}, p {fmt_p(Pr..F.)}"))
  if (to_clip) clipr::write_clip(out$report)
  out
} 


```

# Data prep and descriptive statistics

```{r}
df %<>% mutate(ethn = case_when(
    str_detect(`INFO:E-END`, "White and") ~ "Mixed",
    str_detect(`INFO:E-END`, "Mixed") ~ "Mixed",
    str_detect(`INFO:E-END`, "White") |
      str_detect(`INFO:E-END`, "Irish") ~ "White",
    #str_detect(`INFO:E-END`, "Black") ~ "BAME",
    #`INFO:E-END` %in% c("Indian", "Bangladeshi", "Pakistani") ~ "BAME", 
    is.na(`INFO:E-END`) & is.na(`INFO:E-START`)~ NA_character_,
    str_detect(`INFO:E-START`, "White and") ~ "Mixed",
    str_detect(`INFO:E-START`, "Mixed") ~ "Mixed",
    str_detect(`INFO:E-START`, "White") |
      str_detect(`INFO:E-START`, "Irish") ~ "White",
    str_detect(`INFO:E-START`, fixed("N/A")) ~ NA_character_,
    T ~ "ME"
    )) %>% mutate(ethn = factor(ethn))

#Only TCN delivered cohorts participated in experiment
df <- df %>% filter(Delivery == "TCN")
#Small number of cohorts could not be matched to activity assignments due to name changes - thus not known which activity they experienced
df <- df %>% filter(!is.na(Activity1))

#A: getting to know each other
#B: diversity in society
#C: differences in team

  df$Activity1 %<>% relevel(ref="A")

  df$Activity1 %<>% fct_recode(control = "A", society = "B", team = "C")

#Number of responses (any completion status) to end-of-programme survey
sum(df$resp_end>0)

df <- df %>% filter(resp_end > 0)

#Number of cohorts
df$wave %>% unique() %>% length()

#Measures:
#### VALUING DIVERSITY
## div society better: 
#df$`Q21-END-E` - happy to live in diverse country
#df$`Q22-END-E` - cultural diversity good
## div teams better:
#Q12-END - prefer working in diverse teams
#Q8-END - diverse teams are better
## Comfort talking about differences
#Q18.1-END - comfortable to openly discuss differences in team
#Q17.2-END - important to openly discuss differences in team

#### CONTACT
#Q11-END-E: important to get to know people from other ethnic backgrounds
#Q13.2-END-E: would like more contact with Black British
#Q13.1-END-E: would like more contact with White British
#Q14.2-END-E: will actively approach Black British
#Q14.1-END-E: will actively approach White British
#Q20.2-END-E: only one of your ethnicity in new group - how feel?
#Q41-END: how often discuss commonalities
#Q42-END: how often discuss differences
#Q44-END: how positive/negative contact with participants who are "quite different"

df %<>% rename(pref_div_teams = `Q12-END`, 
               div_teams_better = `Q8-END`, 
               comf_discussing = `Q18.1-END`, 
               imp_discussing = `Q17.2-END`,
               imp_challenging = `Q17.1-END`, 
               cont_quality = `Q44-END`, 
               freq_discuss_differences = `Q42-END`)


df %$% cor.test(pref_div_teams, div_teams_better)
df %$% cor.test(`Q21-END-E`, `Q22-END-E`) #Valuing in society

comf_lookup <- c(1:5)
names(comf_lookup) <- c("Not at all comfortable", "A little comfortable", "Somewhat comfortable", "Quite comfortable", "Very comfortable")
imp_lookup <- c(1:5)
names(imp_lookup) <- c("Not at all important", "A little important", "Somewhat important", "Quite important", "Very important")

df$comf_discussing <- comf_lookup[df$comf_discussing %>% as.character()]
df$imp_discussing <- imp_lookup[df$imp_discussing %>% as.character()]
df$imp_challenging <- imp_lookup[df$imp_challenging %>% as.character()]


df %$% cor.test(`comf_discussing`, `imp_discussing`) #Engaging with diversity
df %$% cor.test(`imp_discussing`, `imp_challenging`) #Importance discussing div and challenging exclusion - I think I intended to pre-register the former


df$val_div_society <- rNuggets::make_scale(df, c("Q21-END-E", "Q22-END-E"), "Valuing diversity in society")
df$val_div_teams <- rNuggets::make_scale(df, c("pref_div_teams", "div_teams_better"), "Valuing diversity in teams")
df$address_diversity <- rNuggets::make_scale(df, c("comf_discussing", "imp_discussing"), "Addressing diversity in team settings")

cont_quality_lookup <- c(1:5)
names(cont_quality_lookup) <- c("Very negative", "Negative", "Neutral", "Positive", "Very positive")
df$cont_quality <- cont_quality_lookup[df$cont_quality %>% as.character()]

approach_lookup <- c(1:5)
names(approach_lookup) <- c("Strongly disagree", "Disagree", "Neutral", "Agree", "Strongly agree")
df$approach_black <- approach_lookup[df$`Q14.2-END-E` %>% as.character()]
df$approach_white <- approach_lookup[df$`Q14.1-END-E` %>% as.character()]

df$approach <- df %$% coalesce(approach_black, approach_white)

freq_lookup <- c(1:5)
names(freq_lookup) <- c("Never", "Rarely", "Sometimes", "Often", "Very often")
df$freq_discuss_differences  <- freq_lookup[df$freq_discuss_differences %>% as.character()]
```


```{r}
n_resp <- function(x) {
  sum(!is.na(x))
}



df$responded_any <- df  %>%
    select(val_div_society, val_div_teams, approach, cont_quality, address_diversity, freq_discuss_differences) %>% {rowSums(!is.na(.))>0}

df %>% group_by(Activity1) %>%
 select(val_div_society, val_div_teams, approach, cont_quality, freq_discuss_differences) %>%filter_all(any_vars(!is.na(.))) %>% summarise_all(n_resp)
  
df$responded <- FALSE

df$responded[!is.na(df$val_div_society)|!(is.na(df$val_div_teams))] <- TRUE

table(df$responded, df$Activity1) %>% prop.table(margin = 2)

sum(df$reponded_any) - sum(df$responded)

chisq.test(df$responded, df$Activity1)
chisq.test(df$responded_any, df$Activity1)

df %<>% filter(responded_any)



df$Activity1 %>% table()



#Ethnic composition
df$ethn %>% table() %>% addmargins()
df$`INFO:E-END` %>% table() %>% sort(decr = TRUE) %>% head(10)
df$ethn %>% table() %>% prop.table()

#Run scale functions again for descriptives
df$val_div_society <- rNuggets::make_scale(df, c("Q21-END-E", "Q22-END-E"), "Valuing diversity in society")
df$val_div_teams <- rNuggets::make_scale(df, c("pref_div_teams", "div_teams_better"), "Valuing diversity in teams")
df$address_diversity <- rNuggets::make_scale(df, c("comf_discussing", "imp_discussing"), "Addressing diversity in team settings")

df  %>%
 select(val_div_society, val_div_teams, approach, cont_quality, address_diversity, freq_discuss_differences) %>% summarise_all(n_resp)

miss_activity <- function(var_char) {
  print(glue_warn("Chi-sq test for association between missingness of {var_char} and condition:"))
  out <- chisq.test(is.na(df %>% select(one_of(var_char))%>%pull()), df$Activity1)
  apa::chisq_apa(out)
  if(out$p.value < .05) print(table(is.na(df[var_char]), df$Activity1) %>% prop.table(margin = 2) %>% round(2))
  invisible(out)
  }

miss_activity("val_div_society")
miss_activity("approach")
miss_activity("val_div_teams")
miss_activity("cont_quality")
miss_activity("address_diversity")
miss_activity("freq_discuss_differences")

```

```{r}
m_sd <- function(x) {
  paste0(sprintf("%0.2f", mean(x, na.rm = T)), " (", sprintf("%0.2f", sd(x, na.rm = T)), ")")
}

Ns <- df %>% select(`Valuing diverse teams` = val_div_teams, `Valuing diverse societies` = val_div_society, `Contact quality` = cont_quality, `Frequency of discussing differences` = freq_discuss_differences,  `Interest in contact` = approach, `Commitment to address diversity` = address_diversity) %>% summarise_all(~sum(!is.na(.x))) %>% t() %>% as.numeric() %>% tibble(`*N*` = .)

 df %>% select(`Valuing diverse teams` = val_div_teams, `Valuing diverse societies` = val_div_society, `Contact valence` = cont_quality, `Frequency of discussing differences` = freq_discuss_differences,  `Interest in contact` = approach, `Commitment to address diversity` = address_diversity) %>% cor_matrix() %>% apa_cor_table(filename = "cor_table.html", extras = Ns)



# Descriptives - all
 d <- df %>% group_by(Activity1) %>% 
        summarise(`*N*` = n(), 
                  `Valuing diverse teams` = m_sd(val_div_teams),
                  `Valuing diverse societies` = m_sd(val_div_society),
                  `Contact valence` = m_sd(cont_quality),
                  `Discussing differences` = m_sd(freq_discuss_differences),
                  `Interest in contact` = m_sd(approach),
                  `Address diversity` = m_sd(address_diversity)) %>% 
   arrange(match(Activity1, c("team", "society", "control"))) %>% rename(Condition = Activity1)
 
 d$Condition <- c("1. Diversity in teams", "2. Diversity in society", "3. Control")  
 
d %>% gt::gt() %>% modelsummary:::fmt_labels_md("column") %>% gt_apa_style()
```


```{r}
#By ethn
d <- df %>% filter(ethn %in% c("White", "ME")) %>% group_by(ethn, Activity1) %>% 
        summarise(`*N*` = n(), 
                  `Valuing diverse teams` = m_sd(val_div_teams),
                  `Valuing diverse societies` = m_sd(val_div_society),
                  `Contact valence` = m_sd(cont_quality),
                                    `Discussing differences` = m_sd(freq_discuss_differences),
                  `Approach intentions` = m_sd(approach),
                  `Commitment to address diversity` = m_sd(address_diversity)) %>%
   arrange(match(Activity1, c("team", "society", "control"))) %>% rename(Condition = Activity1)
 
 d$Condition <- c("1. Diversity in teams", "1. Diversity in teams", "2. Diversity in society","2. Diversity in society", "3. Control", "3. Control")  
 
d %>% gt::gt() %>% modelsummary:::fmt_labels_md("column") %>% gt_apa_style()
 
```

# Inferential tests for main effects

Non-significant ones not really interesting based on descriptive statistics - not reported in detail

```{r}


 lmer((val_div_teams) ~ 1 + (1|wave), data=df) %>% ranova()
 lmer((val_div_society) ~ 1 + (1|wave), data=df) %>% ranova()
 lmer((cont_quality) ~ 1 + (1|wave), data=df) %>% ranova()
 lmer((approach) ~ 1 + (1|wave), data=df) %>% ranova()
 lmer((address_diversity) ~ 1 + (1|wave), data=df) %>% ranova()
 lmer((freq_discuss_differences) ~ 1 + (1|wave), data=df) %>% ranova()

 outcomes <- c("val_div_teams", "val_div_society", "cont_quality", "approach", "address_diversity", "freq_discuss_differences")
 
 reports <- purrr::map_dfr(outcomes, function(outcome) {
   out <- lmer(formula(glue_warn("{outcome} ~ Activity1 + (1|wave)")), data = df) %>% anova(type = 2, ddf = "Ken") %>% report_anova() %>% pull(report)
   tibble(outcome = outcome, report = out)
 })
 
   lmer((freq_discuss_differences) ~ Activity1 + (1|wave), data=df) %>% emmeans::emmeans(list(pairwise ~ Activity1), adjust = "holm")


  hedges_g(df, freq_discuss_differences, Activity1) %>% filter(!str_detect(pair, "_NA")) %>% mutate(report = glue_warn("{round_(g)} {rNuggets:::.fmt_ci(ci.lower, ci.upper)}"))

    lmer((freq_discuss_differences) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME")))  %>% anova(type = 2, ddf = "Ken") %>% report_anova()


```

# Suppression (mediation model)

```{r}
cor.test(df$freq_discuss_differences, df$val_div_society)

df$soc_act <- ifelse(df$Activity1 == "society", 1, 0)

med_mod <- ("
            val_div_society ~ c*soc_act + b*freq_discuss_differences
            freq_discuss_differences ~ a*soc_act
            indirect := a*b
            direct := c
            total := indirect+direct
            ")

library(lavaan)
set.seed(300688)
fit <- sem(med_mod, df, se = "bootstrap", test = "bootstrap", bootstrap = 5000, std.ov = TRUE)

plot_data <- tidy(fit, conf.int = TRUE, boot.ci.type = "perc") %>% select(type = label, pvalue = p.value, est = estimate, ci.lower = conf.low, ci.upper = conf.high)

boot_types <- c("norm", "perc", "bca.simple", "basic")

boot_cis <- purrr::map_dfr(boot_types, function(x){
  tidy(fit, conf.int = TRUE, boot.ci.type = x) %>% filter(label == "indirect") %>% transmute(boot_type = x, ci.lower = conf.low, ci.upper = conf.high)
}) #Based on Hayes & Scharkow (2013), only bc and perc are regularly used, and perc is lavaan default - so kept for now, even though some highlight issues with perc, e.g., https://arxiv.org/pdf/1411.5279.pdf

#Hayes & Sharkow (2013) alternatively recommend MC intervals - again similar
mc <- semTools::monteCarloMed("a*b", object = fit)

#Choice might matter because bootstrap results are very skewed - (which is prob usually the case, given how multiplication works?)
 b %>% data.frame() %>% mutate(ind = a*b) %>% ggplot(aes(ind)) + geom_histogram()

med_model <- tibble::tribble(
  ~type, ~mediator, 
  "a", "Discussing <br /> differences", 
  "b", "Discussing <br /> differences", 
  "direct", NA, 
  "indirect", "Discussing <br /> differences", 
  "total", NA
) %>% left_join(plot_data)

# Run plot command
rNuggets:::plot_mediation(
  IV = "Society-focused <br /> intervention",
  DV = "Valuing diversity <br /> in society", Ms = "Discussing <br /> differences", df = med_model
)


```


# Interaction with ethnicity

```{r}
df %<>% mutate(ActXethn = paste0(Activity1, "_", ethn))



  lmer((val_div_teams) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()
  lmer((val_div_society) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()

  lmer((cont_quality) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()
  lmer((freq_discuss_differences) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME")))  %>% anova(type = 2, ddf = "Ken") %>% report_anova()
  
  lmer((approach) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()
  lmer((address_diversity) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()
  
    
  #lmer((imp_discussing) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()
  #lmer((comf_discussing) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME"))) %>% anova(type = 3, ddf = "Ken") %>% report_anova()

  #Post-hoc
  mod_I <- lmer((val_div_teams) ~ Activity1*ethn + (1|wave), data=df %>% filter(ethn %in% c("White", "ME")))
  emmeans::emmeans(mod_I, list(pairwise ~ Activity1 | ethn), adjust = "holm")

  hedges_g(df %>% filter(ethn %in% c("White", "ME")), val_div_teams, ActXethn) %>% filter(!str_detect(pair, "_NA"))
  


  
```

# Post-hoc comparison

```{r}

## Approach
  #Post-hoc
  vars <- c("approach", "cont_quality", "address_diversity", "freq_discuss_differences")
  


  
  trends <- purrr::map_dfr(vars, function(x){
  out <- lmer(formula(glue_warn("{x} ~ Activity1*ethn + (1|wave)")), data=df %>% filter(ethn %in% c("White", "ME"))) %>%
  emmeans::emmeans(list(pairwise ~ Activity1 | ethn), adjust = "none") %>% extract2(2) %>% data.frame() %>% filter(p.value < .1) %>% transmute(var = x, ethn, contrast, p.value, pair = paste0(str_replace(contrast, " - ", paste0("_", ethn, " & ")), "_", ethn))
  hedges_g(df, sym(x), ActXethn) %>% left_join(out, .)
  })
  
  trends %<>% mutate(report = glue_warn("{round_(g)} {rNuggets:::.fmt_ci(ci.lower, ci.upper)}"))

  trends
  
```

# Interaction plots

```{r}
se <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}

   d <- df %>% filter(ethn %in% c("White", "ME")) %>% group_by(ethn, Activity1) %>% summarise(var = "Interest in contact", M = mean(approach, na.rm = T), SE = se(approach, na.rm = T)) %>% na.omit() %>% bind_rows(
     df %>% filter(ethn %in% c("White", "ME")) %>% group_by(ethn, Activity1) %>% summarise(var = " Contact valence", M = mean(cont_quality, na.rm = T), SE = se(cont_quality, na.rm = T)) %>% na.omit()
   )  %>% bind_rows(
       df %>% filter(ethn %in% c("White", "ME")) %>% group_by(ethn, Activity1) %>% summarise(var = "Address diversity", M = mean(address_diversity, na.rm = T), SE = se(address_diversity, na.rm = T)) %>% na.omit()
   ) %>% bind_rows(
       df %>% filter(ethn %in% c("White", "ME")) %>% group_by(ethn, Activity1) %>% summarise(var = " Discuss differences", M = mean(freq_discuss_differences, na.rm = T), SE = se(freq_discuss_differences, na.rm = T)) %>% na.omit()
   )  %>% 
   arrange(match(Activity1, c("team", "society", "control")))

   annotations_df <- tibble::tribble( #from `trends` dataframe
     ~var, ~y, ~xmin, ~xmax, ~label, ~Activity1,
     "Interest in contact", 4.3, 1.7, 2.3, "p = .044", NA,
     " Discuss differences", 4.3, 1.7, 2.0, "p = .087", NA 
   )
       
 d %>% ggplot(aes(x=ethn, fill=Activity1, y=M)) + 
      geom_col(position = "dodge") + theme_classic() + 
      geom_errorbar(aes(ymin = M-SE, ymax = M+SE), width = .2, position=position_dodge(.9)) +
      labs(x = "Group status", 
           fill = "Activity") + facet_wrap(. ~ var) +
      coord_cartesian(ylim = c(1,5)) + 
      scale_fill_discrete(labels = c("team" = "Teams", "society" = "Society", "control" = "Control"), type = c("grey", "orange", "lightblue")) +
       scale_x_discrete(labels = c("ME" = "Minority-ethnic")) + papaja::theme_apa() + theme(strip.text.x = element_text(face = "bold")) +
      ggsignif::geom_signif(data = annotations_df, aes(y_position=y, xmin=xmin, xmax=xmax, 
                            annotations=label), tip_length=0.1, manual = TRUE) #p-values from `trends` tibble

lmer(formula(freq_discuss_differences ~ Activity1*ethn + (1|wave)), data=df %>% filter(ethn %in% c("White", "ME"))) %>%
  emmeans::emmeans(list(pairwise ~ Activity1 | ethn), adjust = "none") %>% extract2(2) %>% data.frame() %>% dplyr::filter(contrast == "control - society")

hedges_g(df %>% filter(ethn %in% c("White", "ME")), "freq_discuss_differences", "ActXethn") %>% filter(stringr::str_detect(pair, "^control.*society")) %>% mutate(report = glue_warn("{round_(g)} {rNuggets:::.fmt_ci(ci.lower, ci.upper)}"))
 
 #ggsave_show(w=20,h=15)
```



# Separate analyses of diversity items

```{r}
pacman::p_load(ordinal, car, RVAideMemoire, ggeffects)
Anova(model,
      type = "II")

df %<>% mutate(pref_div_teams_factor = factor(pref_div_teams), div_teams_better_factor = factor(div_teams_better))
mydata <- df
clmm(pref_div_teams_factor ~ Activity1 + (1|wave), data = mydata) %>% RVAideMemoire::Anova.clmm(type = "II")
clmm(div_teams_better_factor ~ Activity1 + (1|wave), data = mydata) %>% RVAideMemoire::Anova.clmm(type = "II")

clmm(pref_div_teams_factor ~ Activity1*ethn + (1|wave), data = mydata) %>% RVAideMemoire::Anova.clmm(type = "III")
mod <- clmm(pref_div_teams_factor ~ Activity1*ethn + (1|wave), data = mydata)

clmm(div_teams_better_factor ~ Activity1*ethn + (1|wave), data = mydata) %>% RVAideMemoire::Anova.clmm(type = "III")
clmm(div_teams_better_factor ~ Activity1*ethn + (1|wave), data = mydata) %>% summary()

# Graphing mod

mod_pred <- ggpredict(mod, terms = c("Activity1", "ethn"), type = "fe")
colnames(mod_pred)[c(1, 6, 7)] <- c("Activity", "Response", "Ethnicity")

facets <- c(ME = "Minority-ethnic", White = "White")
legend <- c(ME = "Minority-ethnic", White = "White")


p <- ggplot(mod_pred, aes(x = Response, y = predicted)) +
  geom_point(aes(color = Activity), position = position_dodge(width = 0.5)) +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high, color = Activity), position = position_dodge(width = 0.5), width = 0.3) +
  facet_wrap(~Ethnicity, labeller = labeller(Ethnicity=facets)) +
  ggtitle("Impact of activities on preference for diverse teams by ethnicity") +
  ylab("Predicted probability") +
  theme_minimal() +
  theme(
    strip.background = element_rect(
      fill = "grey", color = "grey"
    ),
    strip.text.x = element_text(
      face = "bold"
    ),
    panel.background = element_rect(fill = NA, color = "grey")
  ) + scale_color_discrete(labels = stringr::str_to_title)

p

ggplot2::ggsave("Figure3_prop_odds.png", width = 20, height = 12, units = "cm")


```


# Chart - diverse teams

```{r}
se <- function(x, na.rm=FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x)/length(x))
}

   d <- df %>% group_by(Activity1, ethn) %>% summarise(M = mean(val_div_teams, na.rm = T), SE = se(val_div_teams, na.rm = T)) %>% na.omit()
   d1 <- df %>% group_by(Activity1) %>% summarise(M = mean(val_div_teams, na.rm = T), SE = se(val_div_teams, na.rm = T)) %>% na.omit()
    d1$ethn = "All"
    dp <- dplyr::bind_rows(d, d1)
    
p <-    dp %>% ggplot(aes(x=Activity1, fill=ethn, y=M)) + 
      geom_col(position = "dodge") + theme_classic() + 
      geom_errorbar(aes(ymin = M-SE, ymax = M+SE), width = .2, position=position_dodge(.9)) +
      labs(x = "Condition", y = "Valuing diverse teams", 
           fill = "Group status") +
      coord_cartesian(ylim = c(1,5)) + 
      scale_x_discrete(labels = c("team" = "Teams", "society" = "Society", "control" = "Control")) +
       scale_fill_discrete(labels = c("ME" = "Minority-ethnic"), type = c("grey", "orange", "lightblue")) +
      ggsignif::geom_signif(y_position=c(3.5, 3.5, 4, 4.5), xmin=c(2.0, 1, 1, 1), 
                            xmax=c(2.3, 1.3, 2, 3), 
                            annotation=c("p = .036", "p = .073", "p = .024", "p = .024"), tip_length=0.1)  + papaja::theme_apa()



p

ggplot2::ggsave("Figure1_teams.png", width = 20, height = 12, units = "cm")

```

# Chart - diverse society

Not included in write-up - flat line does not need to be visualised

```{r}
se <- function(x, na.rm = FALSE) {
  if (na.rm) x <- na.omit(x)
  sqrt(var(x) / length(x))
}

d <- df %>%
  group_by(Activity1, ethn) %>%
  summarise(M = mean(val_div_society, na.rm = T), SE = se(val_div_teams, na.rm = T)) %>%
  na.omit()
d1 <- df %>%
  group_by(Activity1) %>%
  summarise(M = mean(val_div_society, na.rm = T), SE = se(val_div_teams, na.rm = T)) %>%
  na.omit()
d1$ethn <- "All"
dp <- dplyr::bind_rows(d, d1)

p <- dp %>% ggplot(aes(x = Activity1, fill = ethn, y = M)) +
  geom_col(position = "dodge") +
  theme_classic() +
  geom_errorbar(aes(ymin = M - SE, ymax = M + SE), 
                width = .2, position = position_dodge(.9)) +
  labs(
    x = "Condition", y = "Valuing diversity in society",
    fill = "Group status"
  ) +
  coord_cartesian(ylim = c(1, 5)) +
  scale_x_discrete(labels = c("team" = "Teams", "society" = "Society", "control" = "Control")) +
  scale_fill_discrete(labels = c("ME" = "Minority-ethnic"), type = c("grey", "orange", "lightblue")) +
  papaja::theme_apa()



p

ggplot2::ggsave("Figure2_societies.png", width = 20, height = 12, units = "cm")

```

# Facilitator feedback - implementation check

```{r}
#Contact Lukas Wallrich (l.wallrich@gold.ac.uk) to access the data
facilitators <- read_csv('MentorSurvey_diversity.csv') %>% as.data.frame()

facilitators <- facilitators %>% mutate(Activity = factor(Activity), Close = factor(Close), Engaged = case_when(
  Engaged == "Very disengaged" ~ 1,
  Engaged == "Rather disengaged" ~ 2,
  Engaged == "Rather engaged" ~ 3,
  Engaged == "Very engaged" ~ 4,
  TRUE ~ NA_real_))


table(facilitators$Close) %>% prop.table() %>% `*`(100) %>% round(1)

table(facilitators$Close, facilitators$Activity) %>% prop.table(margin = 2) %>% `*`(100) %>% round(1)
chisq.test(facilitators$Close, facilitators$Activity)

facilitators %>% group_by(Activity) %>% summarise(mean(Engaged, na.rm = TRUE))
lm(Engaged ~ Activity, facilitators) %>% summary()

m_sd(facilitators$Engaged)


```

# For possible later exploration - Bayesian

Bayesian tests could maybe quantify impact of lack of power?

```{r}

df_WME <- df %>% filter(ethn %in% c("White", "ME"))
df_WME$wave2 <- df_WME$wave %>% factor() %>% as.numeric() %>% factor() #Fix issue with embedded nul in string

pacman::p_load(rstanarm, emmeans, bayestestR, logspline, BayesFactor)
anovaBF(val_div_teams ~ Activity1*ethn + wave2, data = df_WME %>% drop_na(val_div_teams), whichRandom = "wave2")

summary(aov(val_div_teams ~ Activity1*ethn + Error(wave2/Activity1), data = df_WME))

stan_model <- stan_lmer(approach ~ Activity1*ethn + (1 | wave), data = df_WME)           # Using default priors
c_activity_main <- pairs(emmeans(stan_model, ~ Activity1))
em_ethn_simple <- emmeans(stan_model, ~Activity1 * ethn)

c_activity_ethn_interaction <- contrast(em_ethn_simple, interaction = c("pairwise","pairwise"))

c_activity_all <- rbind(c_activity_main, c_activity_ethn_interaction)

describe_posterior(c_activity_all,
                   estimate = "median", dispersion = TRUE,
                   ci = .9, ci_method = "hdi",
                   test = c("bayesfactor"),
                   bf_prior = stan_model)

bayes_factors <- purrr::map(vars, function(x){
  print(glue_warn("Bayes factors for {x}:"))
  out <- anovaBF(formula(glue_warn("{x} ~ Activity1*ethn + wave2")), data = df_WME %>% drop_na(sym(x)), whichRandom = "wave2")
  print(out)
})

```

